Paper Report

### 2017-10-13 Paper_report.tex
What does Attention to NMT pay attention

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{IBM models}
\section{Unsupervised Neural HMMs \citep{Tran16unsupervised}}
\section{What does Attention in NMT pay Attention to ? \citep{Ghader2017what} }
\subsection{Main idea}
This research compares between Attention Models (Non-recurrent attention model and Input-feeding model) and Word soft Alignment.
The result is that their differences depends on the word being generated.
\subsection{How to compare ?}
Higher consistency between Attention and Alignment leading to better translation.

>>>>

%----------------------------------------------------------------------------------------
%	IBM models
%----------------------------------------------------------------------------------------

\section{IBM models}

%----------------------------------------------------------------------------------------
%	Unsupervised Neural HMMs
%----------------------------------------------------------------------------------------

\section{Unsupervised Neural HMMs \citep{Tran16unsupervised}}

%----------------------------------------------------------------------------------------
%	What does Attention in NMT pay Attention to ?
%----------------------------------------------------------------------------------------

\section{What does Attention in NMT pay Attention to ? \citep{Ghader2017what} }
\subsection{Main idea}
This research compares between Attention Models (Non-recurrent attention model/ Global attention and Recurrent attention/ Input-feeding model) and known Word Alignment.
The result is that their differences depends on the word type being generated.
\subsection{How to compare ?}
Higher consistency between Attention and Alignment leading to better translation.

\begin{itemize}
\item \textbf{Spearman's rank correlation between attention quality} (Attention loss compared known human alignment) \textbf{and translation quality} (Word prediction loss).
Higher correlation means a closer relationship between translation quality and consistency of attention versus alignment.
	\begin{itemize}
	\item Attention loss
	\item Word prediction loss
	\end{itemize}
\item Attention concentration: Entropy of attention distribution (Soft-hard attention problem)
\end{itemize}

\subsection{Analysis}
The analysis is based on POS tags experiments.
\begin{itemize}
\item Impact of Attention between Non-recurrent (NR) and Recurrent attention (IF): IF has lower AER (Hard attention) and Attention loss (Soft attention).
\item Translation quality: Consistency between attention and word alignment depends on POS tags. For example,
	\begin{itemize}
	\item There is a higher consistency in the case of nouns. However, attention captures other information in the case of verbs.
	\item Translation quality of Verbs is better than Nouns. It means attention does not follow alignment for translating Verbs.
	\end{itemize}
\item Attention concentration: Review the case of Verbs and Nouns.
	\begin{itemize}
	\item Nouns have a lower attention entropy (Higher concentration), lower attention loss (Closer to Alignment), which is that attention entropy can be used as a measure of closeness of attention to alignment in the case of nouns
	\item Verbs have a lower correlation between attention entropy and word prediction loss, which means that attention concentration is not necessary for translating verbs.
	\end{itemize}
\item Attention distribution: It shows how a POS tag of target sentence depends on other POS tags of source sentence.
\end{itemize}

%----------------------------------------------------------------------------------------
%	What does Attention in NMT pay Attention to ?
%----------------------------------------------------------------------------------------

\section{Confidence through Attention \citep{Rikters2017confidence}}
\subsection{Main idea}
